Palaeodistribution of crop progenitors and wild foods in the Southern Levant

### 2023-08-03 analysis/analysis.Rmd
Simplify training data extraction
Fix model prediction

```{r training-climate}
occ |>
  mutate(bio = extract_points(climate$cur, occ$geometry)) |>
  unpack(bio) ->
  occ
```

@@

```{r model}
# TODO: Deal with missing values
rand_forest(mode = "regression") |>
  fit(as.numeric(present) ~ ., data = select(occ, present, starts_with("bio_"))) ->
  rf_fit
```

@@

```{r predict}
predict(rf_fit, climate$cur)
```

>>>>

```{r training-climate}
occ <- cbind(occ, st_extract(climate$cur, occ))
```

@@

```{r model}
# TODO: Where do the missing value(s) actually come from?
occ |>
  as_tibble() |>
  select(present, starts_with("bio")) |>
  drop_na() ->
  rf_data

rand_forest(mode = "regression") |>
  fit(as.numeric(present) ~ ., data = rf_data) ->
  rf_fit
```

@@

```{r predict}
rf_pred <- predict(climate$cur, rf_fit)
```
